Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-12-29 manuscript/manuscript.tex
No inflection point for exponential

We analyse exponential density functions (Eq.~\ref{eq:density-exp}) with values of $b$ equal to
1, 2, 5, 10, 30 and 100, and sinusoidal density functions (Eq.~\ref{eq:density-sine}) with
values of $b$ equal to 1, 2, 5, and 10.
We then apply the density-based discretization algorithm on each function and record the
number divisions carried out.
Figs.~\ref{fig:number-of-tesseroids}(a) and~\ref{fig:number-of-tesseroids}(b) show the
exponential and sinusoidal density functions and the resulting discretization points as
orange dots.

For the exponential density functions, the algorithm performs a single division on the
inflection point independently of the value of $b$.
Therefore, the computation time would likely be at least twice that of the homogeneous
density case (assuming equal implementations).
On the other hand, Fig.~\ref{fig:number-of-tesseroids}c shows an almost linear relation
between the number of divisions in the sinusoidal density case and the value of $b$.
Thus, the computation time is likely to be dependent on the number of wavelengths
of the sinusoidal function that are contained within the tesseroid.

>>>>

We analyse exponential density functions (Eq.~\ref{eq:density-exp}) with values of $b$
equal to 1, 2, 5, 10, 30 and 100, and sinusoidal density functions
(Eq.~\ref{eq:density-sine}) with values of $b$ equal to 1, 2, 5, and 10.
We then apply the density-based discretization algorithm on each function and record the
number divisions carried out.
Figs.~\ref{fig:number-of-tesseroids}a and~\ref{fig:number-of-tesseroids}b show the
exponential and sinusoidal density functions and the resulting discretization points as
orange dots.

For the exponential density functions, the algorithm performs a single division
independently of the value of $b$.
Therefore, the computation time would likely be at least twice that of the homogeneous
density case (assuming equal implementations).
On the other hand, Fig.~\ref{fig:number-of-tesseroids}c shows an almost linear relation
between the number of divisions in the sinusoidal density case and the value of $b$.
Thus, the computation time is likely to be dependent on the number of wavelengths
of the sinusoidal function that are contained within the tesseroid.
